---
title: "Male/Female Bargaining Power and Child Growth"
author: "Bastiaan Quast"
date: "April 11, 2016"
output:
  ioslides_presentation:
    smaller: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.path='../misc/rmd-',
                      cache.path='../data/cache/rmd-',
                      fig.height=3)

load(file = '../data/merged.RData')  # load source  data
load(file = '../data/results.RData')
library(plm)
library(dplyr)
library(ggplot2)
library(printr) # load (customised) printr package for clean output of lm()
```

## Introduction

### Context

* bargaining power vs. household as a unit
* income as bargaining power
* CCTs, UCTs, etc.

### Natural experiment

* state pension income and change in pension eligibility age for men (2010)

### State pension

* general criteria: age and income -> little selection bias
* high nominal value -> general household source of income


## Data

### Dataset

* South Africa: National Income Dynamics Survey
* waves in 2008, 2012, and 2013

### Data

* food expenditure: `expf`
* Z-scores: `zwfa`/`zhfa` (Weight-for-Age (WAZ) / Height-for-Age (HAZ))
* household members (over 60/65) 
* household income
* boy / girl


## Empirical Methodology

### Identification strategy

* event dummy `post_treatment`
* age dummies `man_60_65`, `woman_60_65`, etc.
* Difference-in-Differences: `post_treatmentTRUE:man_60_65TRUE`
* household income covariate (isolate bargaining effect): `hhincome` 

### Specifics

* other covariates: `woman`
* high turnover (both sides): pooled estimation
* R package: `plm`


## Results Food Expenditure

```{r print-expf, echo=FALSE, cache=TRUE}
summary(expf2)$coef
```


## Results Weight-for-Height

```{r print-zwfa, echo=FALSE, cache=TRUE}
summary(zwfa9)$coef
```


## Results Weight-for-Height II

```{r plot-zwfa, warning=FALSE, cache=TRUE}
NIDS %>%
  group_by(wave, man_60_65) %>%
  summarise( zwfa=mean(zwfa, na.rm=TRUE) ) %>%
  ggplot( aes(x=wave, y=zwfa, fill=man_60_65) ) %+%
  geom_bar(stat='identity') %+% 
  facet_grid(~man_60_65)
```


## Results Height-for-Age

```{r print-zhfa, echo=FALSE, cache=TRUE}
summary(zhfa7)$coef
```

## In conclusion

### Results

* positive effect on food expenditure
* positive effect on Weight-for-Age
* negative effect on Height-for-Age

### Conclusion

* might be more but lower nutritional value

### Possible lesson

* food expenditure might be misleading an indicator
