---
title: "Male/Female Bargaining Power and Child Growth"
author: "Bastiaan Quast"
date: "April 11, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.path='../misc/rmd-',
                      cache.path='../data/cache/rmd-',
                      fig.height=3)

load(file = '../data/merged.RData')  # load source  data

library(ggplot2)
library(printr) # load (customised) printr package for clean output of lm()

```

## Introduction

* bargaining power vs. household as a unit
* income as bargaining power
* CCTs, UCTs, etc.

* Pension income and change in pension eligibility age for men


## Data

* South Africa: National Income Dynamics Survey
* Waves in 2008, 2012, and 2013


## Empirical Methodology

* Age dummies `man_60_65`, `woman_60_65`, etc.
* Difference-in-Differences
* Household income covariate: isolate bargaining effect
* 

## Results Food Expenditure


## Results Weight-for-Height

## Results Weight-for-Height II

```{r plot-zwfa}
NIDS %>%
  filter( !is.na(c_woman) ) %>%
  group_by(wave, c_woman) %>%
  summarise(man_60_65=sum(man_60_65)) %>%
  ggplot(aes(x=wave, weight=man_60_65, fill=c_woman)) + 
  geom_bar(position='dodge')
```

## Results Height-for-Age

## Conclusion

* Positive effect on food expenditure
* Positive effect on Weight-for-Age
* Negative effect on Height-for-Age

* Might be more but lower nutritional value

* Food expenditure might be misleading an indicator
