---
title: "Male/Female Bargaining Power and Child Growth"
author: "Bastiaan Quast"
date: "April 11, 2016"
output:
  ioslides_presentation:
    smaller: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.path='../misc/rmd-',
                      cache.path='../data/cache/rmd-',
                      fig.height=3)

load(file = '../data/merged.RData')  # load source  data
load(file = '../data/results.RData')
library(plm)
library(dplyr)
library(ggplot2)
library(printr) # load (customised) printr package for clean output of lm()

```

## Introduction

* bargaining power vs. household as a unit
* income as bargaining power
* CCTs, UCTs, etc.

* Pension income and change in pension eligibility age for men


## Data

* South Africa: National Income Dynamics Survey
* Waves in 2008, 2012, and 2013


## Empirical Methodology

* Age dummies `man_60_65`, `woman_60_65`, etc.
* Difference-in-Differences
* Household income covariate: isolate bargaining effect
* 

## Results Food Expenditure

```{r print-expf, echo=FALSE, cache=TRUE}
summary(expf2)$coef
```

## Results Weight-for-Height

```{r print-zwfa, echo=FALSE, cache=TRUE}
summary(zwfa9)$coef
```

## Results Weight-for-Height II

```{r plot-zwfa, warning=FALSE, cache=TRUE}
NIDS %>%
  group_by(wave, man_60_65) %>%
  summarise( zwfa=mean(zwfa, na.rm=TRUE) ) %>%
  ggplot( aes(x=wave, y=zwfa, fill=man_60_65) ) %+%
  geom_bar(stat='identity') %+% 
  facet_grid(~man_60_65)
```

## Results Height-for-Age

```{r print-zhfa, echo=FALSE, cache=TRUE}
summary(zhfa7)$coef
```

## In conclusion

Results

* Positive effect on food expenditure
* Positive effect on Weight-for-Age
* Negative effect on Height-for-Age

Conclusions

* Might be more but lower nutritional value

Possible lessons

* Food expenditure might be misleading an indicator
